---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# First Take Palettes

This package provides color palettes based on Sony's 
[THE FIRST TAKE](https://www.youtube.com/channel/UC9zY_E8mcAo_Oq772LEZq8Q) video series.
**This package is not affiliated with Sony whatsoever.**

**ftpalsというパッケージのことはソニーやTHE FIRST TAKEに提携していません。**

Current counts:
```{r counts, echo = FALSE, message=FALSE, warning=FALSE}
library(ftpals)
library(dplyr)
library(knitr)
first_takes %>% 
  dplyr::group_by(type) %>% 
  dplyr::summarize(n = dplyr::n()) %>% 
  knitr::kable()
```



## Goals

I made this as a side project to learn more about working with colors in R.
Specifically I wanted to do the following:

 - Learn more about working with image data in R (but.. not using magick)
 - Try to use clustering as a means to make color palettes
 - Try to make those color palettes color blind friendly procedurally
 
There are packages that provide functionality to create color palettes from
images already, such as [colorfindr](https://github.com/zumbov2/colorfindr) and
[paletter](https://github.com/AndreaCirilloAC/paletter) but I wanted to try
something new myself.

I reimplimented the genetic algortihm implementation in this paper:

[Troiano, Luigi & Birtolo, Cosimo & Miranda, Maria. (2008). Adapting palettes to color vision deficiencies by genetic algorithm. GECCO'08: Proceedings of the 10th Annual Conference on Genetic and Evolutionary Computation 2008. 1065-1072. 10.1145/1389095.1389291.](https://www.researchgate.net/publication/220740835_Adapting_palettes_to_color_vision_deficiencies_by_genetic_algorithm)

As a result I learned about genetic algorithms using the `GA` package:

[Luca Scrucca (2013). GA: A Package for Genetic Algorithms in R. Journal of Statistical Software, 53(4), 1-37.](http://www.jstatsoft.org/v53/i04/)

[Luca Scrucca (2017). On some extensions to GA package: hybrid optimisation, parallelisation and islands evolution. The R Journal, 9/1, 187-206.](https://journal.r-project.org/archive/2017/RJ-2017-008)


I used thumbnails from THE FIRST TAKE's YouTube uploads as a test case, as
they often have a nice variety of colors from participants' clothes and the
characteristic bar the studio overlays onto each image. That said, only videos
from THE FIRST TAKE or THE HOME TAKE series were used, not THE FIRST TAKE FES.

## Documentation

The source files used for scraping the video metadata are available in the `R/`
folder and prepended with `scrape_`. The files used to implement the genetic
algorithm are prepended with `GA_`. Note that these aren't exported by the package
though, but they're available to look at or fork. I do provide the `create_palette()`
function that will generate a new palette for a given YouTube video ID (the part
that comes after `watch?v=` in the URL). This function isn't limited to
THE FIRST TAKE videos, it should work for any YouTube video. This package
only needs RCurl to download data, it doesn't use rvest or the YouTube API.

I won't strongly commit to the actual effectiveness of every palette, but I
think some turned out nice!

## Installation

You can install the released version of `ftpals` from github with:

``` r
devtools::install_github("tsostarics/ftpals")
```

# Palette Examples

All palettes are provided by the `ftpals::first_takes` table. This provides
additional metadata such as `videoId`, `artist` name, and `song` title. Note
that some artist/song names are given in Japanese while some are given in Romaji,
this is just how the data got scraped. It seems like if an English translation
is provided for a video, then download requests from the United States will pull
the translation instead of the original Japanese.

`show_pals(i)` will show the two palettes available for a given index in the
`first_takes` table. The original sampling of colors, `first_takes$palette`,
is shown on top, and the "optimized" palette, `first_takes$optimized_palette`,
is shown on the bottom for comparison. The "optimized" palette should be a little
better for those with colorblindness, but effectiveness varies by palette. Due
to the implementation the optimized palette tends to have these qualities:

 - The first color is less white than the original sample
 - The second color is less black than the original sample
 - The palette is **reordered by luminance**, so the hue ordering sometimes changes
 - The palette is often somewhat less saturated than the original palette


Here is an example from 
[this video.](https://www.youtube.com/watch?v=Wdll9P9icJU) You can use the 
`plot_ftpalette()` function to plot the palettes with the thumbnail the colors
were sampled from. Or, you can use `show_pals` to see the two palettes with their
hex codes.
```{r example}
library(ftpals)
library(ggplot2)
plot_ftpalette(91, show_thumbnail = T, use_theme = ggplot2::theme_minimal)
show_pals(91) # 病身を噛む by ずっと真夜中でいいのに
```


Here are a few other examples.
```{r other examples}
show_pals(27) # ミカヅキ by さユり

show_pals(42) # sabotage by 緑黄色社会

show_pals(23) # BL by QUEEN-BEE

show_pals(take = 86) # オーケストラ by AiNA THE END
```

Here's an example with a plot. You can pick the palette you want by
directly indexing the palette or optimized palette you want. Notice there's also
a `bar_color` column you can access for an additional highlight color (it tends
to be a very saturated color).

```{r plot example}
diamonds %>% 
  ggplot(aes(x = cut, y = carat, fill = cut)) +
  stat_summary(fun = 'mean',
               geom = 'bar',
               color = 'black') +
  scale_fill_manual(values = first_takes$optimized_palette[[23]]) +
  geom_hline(yintercept = .75,
             size = 2, 
             linetype = "dashed", 
             color = first_takes$bar_color[[23]]) +
  theme_minimal()
```

## Scale_ functions

You can use `scale_fill_ftake()` and `scale_color_ftake()` to set colors, too.
They take either an `index`, or a `type` character denoting which series of videos
to use and a `take` for which specific video to use. If you want to use palettes
from THE HOME TAKE, you should opt for the type/take method. If you want to use
videos from THE FIRST TAKE, index works fine but there is no video number 70
(either it was accidentally skipped or later taken down), so the index-take 
number correspondence is off by one after 69.

```{r plot example functions}
diamonds %>% 
  ggplot(aes(x = cut, y = carat, fill = cut)) +
  stat_summary(fun = 'mean',
               geom = 'bar',
               color = 'black') +
  scale_fill_ftake(index = 24) +
  geom_hline(yintercept = .75,
             size = 2, 
             linetype = "dashed", 
             color = barcolor(24)) +
  theme_minimal()

diamonds %>% 
  ggplot(aes(x = cut, y = carat, fill = cut)) +
  stat_summary(fun = 'mean',
               geom = 'bar',
               color = 'black') +
  scale_fill_ftake(index = 24, order = 6:1) +
  geom_hline(yintercept = .75,
             size = 2, 
             linetype = "dashed", 
             color = barcolor(24)) +
  theme_minimal()

diamonds %>% 
  ggplot(aes(x = cut, y = carat, fill = cut)) +
  stat_summary(fun = 'mean',
               geom = 'bar',
               color = 'black') +
  scale_fill_ftake(palette = 2, type = "H", take = 10) +
  geom_hline(yintercept = .75,
             size = 2, 
             linetype = "dashed", 
             color = barcolor(type = "H", take = 10)) +
  theme_minimal()
```
